---
title: "Imputation for each method"
author: "Xuwen Liu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    number_sections: true
vignette: >
  %\VignetteIndexEntry{"Imputation for each method"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r dependencies, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(eval = FALSE)
library(MissImp)
```

In the first session of "Generate data", a complete mix-type dataset is first generated with 5 continuous variables, 1 integer variable and 2 categorical variables. Then given the desired missing data proportion and the missing data mechanism, based on the complete dataset, an incomplete dataset with missing values is created. 

Then in the second part of this document "Single Imputation", several imputation methods are shown separately to replace the missing part with predictions in the generated incomplete dataset. For the categorical variable, both the final result and the predicted probability of each category are presented. 

# Generate data

We generate a complete data set $(Y1, Y2, Y3, Y4, Y5, Y6, Y7, Y8)$ with $(Y1, Y2, Y3) \sim \mathcal{N}(\mu_u1, \Sigma_1)$, (Y4, Y5)~N(u2,S2), Y6~P(\lambda) and Y7,Y8~Binomial(prob). 

```{r Generate_complete_dataframe}
n <- 10000
complete_df_generator <- function(n) {
  mu.X <- c(1, 2, 3)
  Sigma.X <- matrix(c(
    9, 3, 2,
    3, 4, 0,
    2, 0, 1
  ), nrow = 3)
  X.complete.cont <- MASS::mvrnorm(n, mu.X, Sigma.X) # multivariate normal distribution

  mu1.X <- c(9, 8)
  Sigma1.X <- matrix(c(
    16, 14,
    14, 25
  ), nrow = 2)

  X.complete.cont1 <- MASS::mvrnorm(n, mu1.X, Sigma1.X) # multivariate normal distribution

  lambda <- 4.3
  X.complete.discr <- stats::rpois(n, lambda) # poisson distribution

  X.complete.cat <- stats::rbinom(n, size = 5, prob = 0.4) # binomial

  X.complete.cat2 <- stats::rbinom(n, size = 7, prob = 0.6) # binomial

  X.complete <- data.frame(cbind(X.complete.cont, X.complete.cont1,
    X.complete.discr,
    ... = X.complete.cat, X.complete.cat2
  ))
  X.complete[, 7] <- as.factor(X.complete[, 7])
  levels(X.complete[, 7]) <- c("F", "E", "D", "C", "B", "A")
  X.complete[, 8] <- as.factor(X.complete[, 8])
  colnames(X.complete) <- c("Y1", "Y2", "Y3", "Y4", "Y5", "Y6", "Y7", "Y8")
  return(X.complete)
}
```

We could generate incomplete dataframe from the complete dataframe, with a chosen percentage of missing data and a chosen missing mechanism. The difference between mechanisms is explained in the documentation of \code{generate_miss}.

```{r add_missingness}
n <- 10000
mech <- "MAR1"
miss_prop <- 0.4
X.complete <- complete_df_generator(n)
rs <- generate_miss(X.complete, miss_prop, mechanism = mech)
df <- rs$X.incomp
```


# Single Imputation

## EM

```{r em}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.em <- em_mod(df_with_mv, col_cat = col_cat)
head(imp.em$ximp)
head(imp.em$ximp.disj)
```



## Missforest

```{r MissForest_boot}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.forest <- missForest_mod(xmis = df, maxiter = 3, ntree = 100, col_cat = col_cat)
head(imp.forest$ximp)
head(imp.forest$ximp.disj)
```


## MissRanger

```{r MissRanger}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.ranger <- missRanger_mod(df_with_mv, col_cat = c(7:8), maxiter = 3)

head(imp.ranger$ximp)
head(imp.ranger$ximp.disj)
```

## MissMDA

```{r MissMDA}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.pca = imputeFAMD_mod(df_with_mv, ncp = 3, maxiter = 30)
head(imp.pca$completeObs)
head(imp.pca$tab.disj)
```

## KNN

```{r kNN}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.knn <- kNN_mod(df_with_mv, col_cat = c(7:8))
head(imp.knn$ximp)
head(imp.knn$ximp.disj)
```



# Multiple Imputation

## MI EM Amelia

```{r MIEM}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.em.mi <- MI_EM_amelia(df_with_mv, col_num = c(1:6), col_cat = col_cat, num_imp = 3)
head(imp.em.mi$ximp)
head(imp.em.mi$ximp.disj)
```

## MI mice

```{r mice}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
res <- mice::mice(df_with_mv, m=3)
imp.mice <- result_mice(res, 3, col_cat=c(7,8))

head(imp.mice$ximp)
head(imp.mice$ximp.disj)
```



## MI PCA

```{r MIPCA}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.pca.mi <- MIFAMD_mod(df_with_mv, ncp=3, maxiter = 50, nboot = 3)
head(imp.pca.mi$ximp)
head(imp.pca.mi$ximp.disj)
```

## MI MissRanger

```{r MI Ranger}
df_with_mv <- df
col_cat <- c(7,8)
df_with_mv <- factor_ordinal_encode(df_with_mv, col_cat)
imp.ranger.mi <- MI_missRanger(df_with_mv, col_cat = c(7,8), num_mi = 3)

head(imp.ranger.mi$ximp)
head(imp.ranger.mi$ximp.disj)
```
