---
title: "MissImp Test"
author: "Xuwen Liu"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    number_sections: true
vignette: >
  %\VignetteIndexEntry{"MissImp Test"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r dependencies, message=FALSE, warning=FALSE}
library(stats)
library(MissImp)
# knitr::opts_chunk$set(eval = FALSE)
```

# Test on the abalone data
In the package, 100 rows of the abalone dataset is stored to test different functions.

```{r load_data}
load('../data/test_abalone.rda')
```

```{r preprocessing_abalone}
abalone_data <- data.frame(test_abalone)
col_num <- c(1:8)
col_dis <- c(8)
col_cat <- c(9)
for (j in col_num) {
  if (j %in% col_dis) {
    suppressWarnings(abalone_data[, j] <- as.integer(abalone_data[, j]))
  }
  else {
    suppressWarnings(abalone_data[, j] <- as.numeric(abalone_data[, j]))
  }
}
for (j in col_cat) {
  abalone_data[, j][abalone_data[, j] == "?"] <- NA
  suppressWarnings(abalone_data[, j] <- as.factor(abalone_data[, j]))
}
abalone_data <- stats::na.omit(abalone_data)
row.names(abalone_data) <- c(1:nrow(abalone_data))
head(abalone_data)
```
After loading and preprocessing the abalone dataset, we can create incomplete datasets with different mechanisms and proportions of missing data. Here for demonstration we chose the "MAR1" missing data mechanism and 20% missing data percentage. (More details about the generation of missing data could be found in vignette "A_Generate_Missingness_and_Tests_MCAR")

```{r incomplet_data_creation}
X.complete <- abalone_data
mech <- "MAR1"
miss_prop <- 0.3
rs <- generate_miss(X.complete, miss_prop, mechanism = mech)
```

Then a model could be chosen to impute the incomplete dataset. The parameters shown below need to be chosen wisely. 

```{r param_setting}
df <- rs$X.incomp
df_complete <- X.complete
col_cat <- c(9)
col_dis <- c(8)
col_num <- c(1:8)

maxiter_tree <- 10
maxiter_pca <- 200
maxiter_mice <- 10
ncp_pca <- round(ncol(df_complete) / 2)
learn_ncp <- FALSE

num_mi <- 4
n_resample <- 4
n_df <- 5

imp_method <- "MI_Ranger"
resample_method <- "bootstrap"
cat_combine_by <- "onehot"
var_cat <- "wilcox_va"
```

```{r MissImp, include=FALSE}
res <- MissImp(
  df = df,
  imp_method = imp_method,
  resample_method = resample_method,
  n_resample = n_resample,
  col_cat = col_cat,
  col_dis = col_dis,
  maxiter_tree = maxiter_tree,
  maxiter_pca = maxiter_pca,
  ncp_pca = ncp_pca,
  learn_ncp = learn_ncp,
  cat_combine_by = cat_combine_by,
  var_cat = var_cat,
  df_complete = df_complete,
  num_mi = num_mi,
  maxiter_mice = maxiter_mice
)
```

```{r result_MissImp}
head(df)
head(res$imp)
head(res$imp.disj)
head(res$uncertainty)
head(res$uncertainty.disj)
res$MSE
res$F1
```

```{r density_comp_with_mean_imp}
res_mean_imp <- df
col_num <- c(1:8)
col_num_name <- colnames(df)[col_num]
for (y in col_num_name) {
  res_mean_imp[[y]][is.na(res_mean_imp[[y]])] <- mean(res_mean_imp[[y]], na.rm = TRUE)
}


ycol <- "V5"
X.miss <- X.complete
X.miss[!is.na(df)] <- NA
dat <- data.frame(
  y = c(X.complete[[ycol]][rs$R.mask[[ycol]]], res$imp[[ycol]][rs$R.mask[[ycol]]], res_mean_imp[[ycol]][rs$R.mask[[ycol]]]),
  lines = rep(c("complete", "imputed", "mean_imputed"), each = sum(rs$R.mask[[ycol]]))
)
ggplot2::ggplot(dat, ggplot2::aes(x = y, fill = lines)) +
  ggplot2::geom_density(alpha = 0.3) +
  ggplot2::labs(x = ycol)

dat <- data.frame(
  y = c(X.miss[[ycol]][rs$R.mask[[ycol]]] - res$imp[[ycol]][rs$R.mask[[ycol]]], X.miss[[ycol]][rs$R.mask[[ycol]]] - res_mean_imp[[ycol]][rs$R.mask[[ycol]]]),
  lines = rep(c("imputed_error", "mean_imputed_error"), each = sum(rs$R.mask[[ycol]]))
)
ggplot2::ggplot(dat, ggplot2::aes(x = y, fill = lines)) +
  ggplot2::geom_density(alpha = 0.3) +
  ggplot2::labs(x = ycol)

#dat <- data.frame(
#  y = c(X.miss[[ycol]], df[[ycol]]),
#  lines = rep(c("missing", "observed"), each = length(df[[ycol]]))
#)
#ggplot2::ggplot(dat, ggplot2::aes(x = y, fill = lines)) +
#  ggplot2::geom_density(alpha = 0.3) +
#  ggplot2::labs(x = ycol)
```

